---
title: "Assignment 14"
output: html_document
---

**To:** Dr. Colin M. Wasiloff

**From:** Brock Pinagel

**Date:** 7/10/2025

**Subject:** Analysis and Recommendation for Major Manufacturing Facility

Dr. Colin M. Wasiloff,

Analysis results of the major manufacturing facilities daily production records are shown in Figures 1, 2 and Table 3. Results shown in Table 1 indicate machine type 3 worked fewer hours (mean = 5.89) and broke down for longer periods (mean = 1.86) resulting in lower efficiency (mean = 80.53%) than machine type 1. Furthermore, results from Table 1 also indicate machine type 1 worked more hours and broke down for shorter periods (mean = 1.03) resulting in higher efficiency (mean = 92.59%) overall. In addition, Table 1 also shows machine type 2 worked fewer hours than both machine types 1 and 2 (mean = 5.18), spent slightly less time down than machine type 3 (mean = 1.51), and was slightly more efficient than machine type 3 (mean = 83.36%). In conclusion, I recommend that machine types 2 and 3 be replaced with machine type 1 to increase productivity and efficiency, and to reduce downtime.

```{r Install Packages, message=FALSE, warning=FALSE}
library(tidyverse)
library(summarytools)
```

Import case study data

```{r Import}
m4 <- read.csv(file = "Module 4 Assignment.csv")
```

### Tidy the data

**CODE BOOK**

**V1** = MTYPE: 1 = "Machine 1", 2 = "Machine 2". The rated production rate for machine type 1 is 700 parts per minute, machine type 2 is rated at 200 parts per minutes.\
**V2** = PROD: Total parts produced by the machine during the hours that the machine was operating.\
**V3** = HRSWRK: Number of hours that the machine was operating. The machines were scheduled for a shift of 7.75 hours each day.\
**V4** = HRSDOWN: Number of hours the machine was down, or inoperative, for any reason.

Rename variables

```{r Rename Vars}
colnames(m4) <- c('MTYPE', 'PROD', 'HRSWRK', 'HRSDOWN')
```

Pipe m4 data frame into m4.cleaned

```{r Pipe}
m4.cleaned <- m4 %>%
  mutate(EXPECTED = ifelse(MTYPE == 1, HRSWRK*700*60, 
                    ifelse(MTYPE == 2, HRSWRK*200*60, HRSWRK*150*60)))%>%
  mutate(EFFICIENCY = PROD/EXPECTED*100)  %>%
  mutate(MTYPE = recode_factor(.x = MTYPE,
                               '1' = 'Machine 1',
                               '2' = 'Machine 2',
                               '3' = 'Machine 3')) 
```

Select variables for analysis

```{r Var Selection}
m4.stats <- m4.cleaned %>%
  select(MTYPE, EFFICIENCY, HRSWRK, HRSDOWN)
```

Change the Stats presented in first and second optional expressions

```{r Stat Change}
st_options(
  dfSummary.custom.1 = 
    expression(
      paste(
        "Q1 - Q3 :",
        round(
          quantile(column_data, probs = .25, type = 2, 
                   names = FALSE, na.rm = TRUE), digits = 1
        ), " - ",
        round(
          quantile(column_data, probs = .75, type = 2, 
                   names = FALSE, na.rm = TRUE), digits = 1
        )
      )
    )
)
st_options(
  dfSummary.custom.2 = 
    expression(
      paste(
        "Skew, Kur :",
        round(
          skewness(column_data, na.rm = TRUE), digits = 1
        ), " , ",
        round(
          kurtosis(column_data, na.rm = TRUE), digits = 1
        )
      )
    )
)

```

**Figure 1.** Data Frame Summary (Appears in Browser)

```{r dfsummary(), message=FALSE, warning=FALSE}
output.dfS <- m4.stats%>% 
  group_by(MTYPE) %>% 
  dfSummary()
view(output.dfS)
```

**Table 1.** Descriptive Statistics of the Case Study Variables

```{r Descriptive Stats Table}
ds.t <- m4.stats%>% 
  group_by(MTYPE) %>% 
  descr(stats   = c("n.valid", "mean", "sd"),
        transpose  = TRUE) %>%
  tb(order = 3) # 1, 2, 3 make different orders of the variables

ds.t

write.csv(ds.t, file = "ds.t.csv")
```

**Figure 2.** Data Frame Boxplots

```{r Boxplot}
box.c1.efficiency <-m4.stats %>% 
  ggplot(aes(x=MTYPE, y=EFFICIENCY, fill = MTYPE)) +
  geom_boxplot(alpha = .3) +
  geom_jitter(aes(color = MTYPE), alpha = .1) +
  theme_minimal() +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(size=12, angle=0),
        legend.position='none')
box.c1.efficiency


box.c1.hrswrk <-m4.stats %>% 
  ggplot(aes(x=MTYPE, y=HRSWRK, fill = MTYPE)) +
  geom_boxplot(alpha = .3) +
  geom_jitter(aes(color = MTYPE), alpha = .1) +
  theme_minimal() + 
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(size=12, angle=0),
        legend.position='none')
box.c1.hrswrk

box.c1.hrsdwn <-m4.stats %>% 
  ggplot(aes(x=MTYPE, y=HRSDOWN, fill = MTYPE)) +
  geom_boxplot(alpha = .3) +
  geom_jitter(aes(color = MTYPE), alpha = .1) +
  theme_minimal() + 
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(size=12, angle=0),
        legend.position='none')
box.c1.hrsdwn
```

Hide x axis ticks for boxplot 1

```{r Hide axis b1}
b1 <- box.c1.efficiency + 
  ylab("Efficiency (%)") +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        legend.position='none')
b1

```

Hide x axis ticks for boxplot 2

```{r Hide axis b2}
b2 <- box.c1.hrswrk + 
  ylab("Hours Working") +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        legend.position='none')
b2
```

Show x axis ticks

```{r Show axis}
b3 <- box.c1.hrsdwn + 
  ylab("Hours Down") +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(size=10, angle=0),
        legend.position='none')
b3

gridExtra::grid.arrange(
  b1, 
  b2, 
  b3, ncol = 1, nrow = 3)
```
